Job Demands-Resources Model Components through the Lens of O*NET Classifications

### 2023-02-21 Submission.Rmd
updating results section

>Hypothesis 1: Job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource.

>Hypothesis 2: Job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are viewed as both a resource and a demand.

Two exploratory questions further address whether our *literature-implicated* job characteristics (e.g., autonomy) are consistently rated as our research models suggest across the job-demands resources theory [@bakker2017job] and challenge-hindrance stressor framework [@cavanaugh2000empirical].

>*Research Question 1*: Are literature-implicated resources consistently rated as job resources?

>*Research Question 2*: Are literature-implicated demands consistently rated as job demands?

@@

The Occupational Information Network (O\*NET) contains a comprehensive description of occupations [@peterson2001understanding]. This widely accessed database houses hundreds of standardized and occupation-specific descriptors most occupations in the US and these descriptions are continually updated. We used 98 statements/questions from O\*NET [activity and context classifications](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3). We retained work activity classifications which O\*NET groups into categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?). Work context statements were grouped into interpersonal relationships (i.e., this category describes the context of the job in terms of human interaction processes), physical work conditions (i.e., this category describes the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (i.e., this category involves the relationships or interactions between the worker and the structural characteristics of the job).

O\*NET collects information about these categories by periodically asking workers about these statements/questions, which often have [unique response categories](https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2).  For example, "How responsible is the worker for work outcomes and results of other workers?" has response options ranging from *No responsibility* to *Very high responsibility*, while the question, "How often do you use electronic mail in this job?" has options ranging from *Never* to *Every day*. We retained O\*Net’s response scales, several of which were semantically unique across items, but all shared the same 5-point scale. It would likely NOT be considered controversial to referred to these as "effectively" Likert-type response scales. Other than minor grammatical editing (for example, changing “the worker” to “you”), we also retained the O\*Net wording for our item stems (statements/questions).

The total number of items on the survey was less than 392 (98 characteristics x 4 administrations) because we did not ask for demand and resource evaluations for 14 O\*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was *...the extent to which the worker is exposed to radiation on the job*).

@@

Data were collected through Prolific, a data collection platform. An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information. Eligibility requirements included being 18+ and holding either a full-time or part-time job. Participants then voluntarily chose to respond to the survey. The survey was conducted online via Qualtrics with an estimated completion time of 40-45 minutes. Participants were asked to think about their primary job while answering the survey, and the items they were presented with depended on the specific job characteristics they initially specified. Thus, if a respondent indicated that a characteristic was not part of their job, they were not subsequently asked to rate the level of resource (i.e., ...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (i.e., ...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (i.e., ...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order. Participants were compensated for their participation in this study in the amount of six dollars through Prolific.

@@

The first hypothesis asks whether job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource. Figure \@ref(fig:overallhist) presents frequency distributions standard deviations of characteristic perceptions, grouped by whether that characteristic was rated as a resource, challenge, or demand. As can be seen in the figure, there was a wide range of agreement versus disagreement with resources and challenges, but hindrances were almost universally associated with disagreement (Bartlett's $\chi^2_{`r lookie$df`}$ = `r lookie$statistic[[1]]`, *p* = `r lookie$p.value` ).

@@

>>>>

>Hypothesis 1: Job characteristics differ in constancy regarding subjective worker perception as a demand or resource.

>Hypothesis 2: Job characteristics are not exclusively categorized as a resource or demand, but rather, some job characteristics are viewed as both a resource and a demand.

Two exploratory questions further address whether our *literature-implicated* resources (e.g., autonomy) and demands are consistently rated as our research models suggest across the job-demands resources theory [@bakker2017job] and challenge-hindrance stressor framework [@cavanaugh2000empirical].

>*Research Question 1*: Do literature-implicated resources materialize as perceived resources?

>*Research Question 2*: Do literature-implicated demands materialize as job demands?

@@

The Occupational Information Network (O\*Net) contains a comprehensive description of occupations [@peterson2001understanding]. This widely accessed database houses hundreds of standardized and occupation-specific descriptors of most occupations in the US and these descriptions are continually updated. We retained 98 work [activity and context classifications](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3) which O\*Net groups into categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?). Work context statements were grouped into interpersonal relationships (i.e., the context of the job in terms of human interaction processes), physical work conditions (i.e., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (i.e., the relationships or interactions between the worker and the structural characteristics of the job).

O\*Net collects information about these categories by periodically asking workers about these statements/questions, which often have [unique response categories](https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2).  For example, "How responsible is the worker for work outcomes and results of other workers?" has response options ranging from *No responsibility* to *Very high responsibility*, while the question, "How often do you use electronic mail in this job?" has options ranging from *Never* to *Every day*. We retained O\*Net’s response scales, all of which shared the same 5-point scale regardless of semantic label difference. Other than minor grammatical editing (for example, changing “the worker” to “you”), we also retained the O\*Net wording for our item stems (statements/questions).

@@

Data were collected through Prolific, a data collection platform. An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information. Eligibility requirements included being 18+ and holding either a full-time or part-time job. Participants then voluntarily chose to respond to the survey. The survey was conducted online via Qualtrics with an estimated completion time of 40-45 minutes. Participants were asked to think about their primary job while answering the survey, and the items they were presented with depended on the specific job characteristics they initially specified. Thus, if a respondent indicated that a characteristic was not part of their job, they were not subsequently asked to rate the level of resource (i.e., ...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (i.e., ...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (i.e., ...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order. The total number of items on the survey was less than 392 (98 characteristics x 4 repeated measurements) because we did not ask for demand and resource evaluations for 14 O\*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was *...the extent to which the worker is exposed to radiation on the job*).Participants were compensated for their participation in this study in the amount of six dollars through Prolific.

@@

The first hypothesis asks whether job characteristics differ in constancy regarding subjective worker perception as a demand or resource.

@@

Figure \@ref(fig:overallhist) shows that hindrances tend to exhibit similar levels of variability across items. Challenges and resources, however, exhibit items that are rated more similary across people (note the spread of the challenge and resource histograms relative to the hindrance histogram). A Bartlett's test for homogeneity of variance confirms this difference ($\chi^2_{`r lookie$df`}$ = `r lookie$statistic[[1]]`, *p* = `r lookie$p.value` ).

### 2023-02-21 Submission.tex
updating results section

\begin{quote}
Hypothesis 1: Job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource.
\end{quote}

\begin{quote}
Hypothesis 2: Job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are viewed as both a resource and a demand.
\end{quote}

Two exploratory questions further address whether our \emph{literature-implicated} job characteristics (e.g., autonomy) are consistently rated as our research models suggest across the job-demands resources theory (Bakker \& Demerouti, 2017) and challenge-hindrance stressor framework (Cavanaugh et al., 2000).

\begin{quote}
\emph{Research Question 1}: Are literature-implicated resources consistently rated as job resources?
\end{quote}

\begin{quote}
\emph{Research Question 2}: Are literature-implicated demands consistently rated as job demands?
\end{quote}

@@

The Occupational Information Network (O*NET) contains a comprehensive description of occupations (Peterson et al., 2001). This widely accessed database houses hundreds of standardized and occupation-specific descriptors most occupations in the US and these descriptions are continually updated. We used 98 statements/questions from O*NET \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{activity and context classifications}. We retained work activity classifications which O*NET groups into categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?). Work context statements were grouped into interpersonal relationships (i.e., this category describes the context of the job in terms of human interaction processes), physical work conditions (i.e., this category describes the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (i.e., this category involves the relationships or interactions between the worker and the structural characteristics of the job).

O*NET collects information about these categories by periodically asking workers about these statements/questions, which often have \href{https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2}{unique response categories}. For example, ``How responsible is the worker for work outcomes and results of other workers?'' has response options ranging from \emph{No responsibility} to \emph{Very high responsibility}, while the question, ``How often do you use electronic mail in this job?'' has options ranging from \emph{Never} to \emph{Every day}. We retained O*Net's response scales, several of which were semantically unique across items, but all shared the same 5-point scale. It would likely NOT be considered controversial to referred to these as ``effectively'' Likert-type response scales. Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we also retained the O*Net wording for our item stems (statements/questions).

The total number of items on the survey was less than 392 (98 characteristics x 4 administrations) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).

@@

Data were collected through Prolific, a data collection platform. An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information. Eligibility requirements included being 18+ and holding either a full-time or part-time job. Participants then voluntarily chose to respond to the survey. The survey was conducted online via Qualtrics with an estimated completion time of 40-45 minutes. Participants were asked to think about their primary job while answering the survey, and the items they were presented with depended on the specific job characteristics they initially specified. Thus, if a respondent indicated that a characteristic was not part of their job, they were not subsequently asked to rate the level of resource (i.e., \ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (i.e., \ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (i.e., \ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order. Participants were compensated for their participation in this study in the amount of six dollars through Prolific.

@@

The first hypothesis asks whether job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource. Figure \ref{fig:overallhist} presents frequency distributions standard deviations of characteristic perceptions, grouped by whether that characteristic was rated as a resource, challenge, or demand. As can be seen in the figure, there was a wide range of agreement versus disagreement with resources and challenges, but hindrances were almost universally associated with disagreement (Bartlett's \(K^2\) = 76.83, \emph{p} = 0.00 ).

@@

>>>>

\begin{quote}
Hypothesis 1: Job characteristics differ in constancy regarding subjective worker perception as a demand or resource.
\end{quote}

\begin{quote}
Hypothesis 2: Job characteristics are not exclusively categorized as a resource or demand, but rather, some job characteristics are viewed as both a resource and a demand.
\end{quote}

Two exploratory questions further address whether our \emph{literature-implicated} resources (e.g., autonomy) and demands are consistently rated as our research models suggest across the job-demands resources theory (Bakker \& Demerouti, 2017) and challenge-hindrance stressor framework (Cavanaugh et al., 2000).

\begin{quote}
\emph{Research Question 1}: Do literature-implicated resources materialize as perceived resources?
\end{quote}

\begin{quote}
\emph{Research Question 2}: Do literature-implicated demands materialize as job demands?
\end{quote}

@@

The Occupational Information Network (O*Net) contains a comprehensive description of occupations (Peterson et al., 2001). This widely accessed database houses hundreds of standardized and occupation-specific descriptors of most occupations in the US and these descriptions are continually updated. We retained 98 work \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{activity and context classifications} which O*Net groups into categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?). Work context statements were grouped into interpersonal relationships (i.e., the context of the job in terms of human interaction processes), physical work conditions (i.e., the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (i.e., the relationships or interactions between the worker and the structural characteristics of the job).

O*Net collects information about these categories by periodically asking workers about these statements/questions, which often have \href{https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2}{unique response categories}. For example, ``How responsible is the worker for work outcomes and results of other workers?'' has response options ranging from \emph{No responsibility} to \emph{Very high responsibility}, while the question, ``How often do you use electronic mail in this job?'' has options ranging from \emph{Never} to \emph{Every day}. We retained O*Net's response scales, all of which shared the same 5-point scale regardless of semantic label difference. Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we also retained the O*Net wording for our item stems (statements/questions).

@@

Data were collected through Prolific, a data collection platform. An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information. Eligibility requirements included being 18+ and holding either a full-time or part-time job. Participants then voluntarily chose to respond to the survey. The survey was conducted online via Qualtrics with an estimated completion time of 40-45 minutes. Participants were asked to think about their primary job while answering the survey, and the items they were presented with depended on the specific job characteristics they initially specified. Thus, if a respondent indicated that a characteristic was not part of their job, they were not subsequently asked to rate the level of resource (i.e., \ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (i.e., \ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (i.e., \ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order. The total number of items on the survey was less than 392 (98 characteristics x 4 repeated measurements) because we did not ask for demand and resource evaluations for 14 O*Net characteristics that we projected would have very low frequency of endorsement across respondents (one excluded characteristic, for example, was \emph{\ldots the extent to which the worker is exposed to radiation on the job}).Participants were compensated for their participation in this study in the amount of six dollars through Prolific.

@@

The first hypothesis asks whether job characteristics differ in constancy regarding subjective worker perception as a demand or resource.

@@

Figure \ref{fig:overallhist} shows that hindrances tend to exhibit similar levels of variability across items. Challenges and resources, however, exhibit items that are rated more similary across people (note the spread of the challenge and resource histograms relative to the hindrance histogram). A Bartlett's test for homogeneity of variance confirms this difference (\(\chi^2_{}\) = 76.83, \emph{p} = 0.00 ).
